Stats

### 2022-04-06 stats/analysis.Rmd
create saves folder, add webcam coding script

mAgeHedge <- brm(clickDistInBalloons ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
                    data = mDataAgeHedge,
                    family = lognormal(),
                    warmup = 1000, 
                    iter   = 3000, 
                    chains = 4, 
                    inits  = "random",
                    cores  = 4)
```

@@

mAgeBox <- brm(correctBox ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
                    data = mDataAgeBox,
                    family = bernoulli(link = "logit"),
                    warmup = 1000, 
                    iter   = 3000, 
                    chains = 4, 
                    inits  = "random",
                    cores  = 4)
```

@@

```{r save_splithalf_data}
write.csv(splithalf_data, "gafo-splithalf.csv", quote = F, row.names = F)
saveRDS(splithalf_data, file = "gafo-splithalf.rds")
```

@@

@@

```{r retest_hedge_kids}
hedge_retest_kids <- hedge_retest %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = ageInYears), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 4, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
  labs(x = "Testday 1", y = "Testday 2")

@@

@@

# run model
mRetestHedge <- brm(clickDistInBalloons ~ age + (0 + reliday | subjID), 
                              data   = mDataRetestHedge, 
                              family = lognormal(), 
                              warmup = 1000, 
                              iter   = 3000, 
                              chains = 4, 
                              inits  = "random",
                              cores  = 4)
```

@@

# run model
mRetestBox <- brm(correctBox ~ age + (0 + reliday | subjID), 
                              data   = mDataRetestBox, 
                              family = bernoulli(link = "logit"),
                              warmup = 1000, 
                              iter   = 3000, 
                              chains = 4, 
                              inits  = "random",
                              cores  = 4)
```

@@

```{r save_model_output}
# mcor <- model_cor %>%
#     mutate(task = recode(task,
#                     `mutual_exclusivity` = "Mutual Exclusivity",
#                     `informativeness` = "Informativeness Inference (1)",
#                     `simple_inf` = "Informativeness Inference (2)",
#                     `preference` = "Speaker Preference",
#                     `novelty` = "Discourse Novelty",
#                     `card_sorting` = "Card Sorting",
#                     `discourse_continuity` = "Discourse Continuity",
#                     `ad_hoc_implicature` = "Ad-hoc Implicature",
#                     `match_to_sample` = "Relational Match-to-sample"),
#            term = task, 
#            mcor = Estimate, 
#            mcor_lci = `l-95% CI`, 
#            mcor_uci = `u-95% CI`)%>%
#   select(study, term, task, mcor, mcor_lci, mcor_uci)

# saveRDS(mcor, "model_results.rds")
```

>>>>

mAgeHedge <- brm(clickDistInBalloons ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
                    data = mDataAgeHedge,
                    family = lognormal(),
                    warmup = 1000, 
                    iter   = 3000, 
                    chains = 4, 
                    inits  = "random",
                    cores  = 4)

write.csv(mAgeHedge, "../saves/mAgeHedge.csv", quote = F, row.names = F)
saveRDS(mAgeHedge, "../saves/mAgeHedge.rds")
```

@@

mAgeBox <- brm(correctBox ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
                    data = mDataAgeBox,
                    family = bernoulli(link = "logit"),
                    warmup = 1000, 
                    iter   = 3000, 
                    chains = 4, 
                    inits  = "random",
                    cores  = 4)

write.csv(mAgeBox, "../saves/mAgeBox.csv", quote = F, row.names = F)
saveRDS(mAgeBox, "../saves/mAgeBox.rds")
```

@@

```{r save_splithalf_data}
write.csv(splithalf_data, "../saves/gafo-splithalf.csv", quote = F, row.names = F)
saveRDS(splithalf_data, file = "../saves/gafo-splithalf.rds")
```

@@

# calculate at which values we would start seing data as outliers
hedge_retest %>% 
  summarize(
    lower_reliday1 = mean(mean_reliday1) - 3*sd(mean_reliday1), 
    upper_reliday1 = mean(mean_reliday1) + 3*sd(mean_reliday1),
    lower_reliday2 = mean(mean_reliday2) - 3*sd(mean_reliday2),
    upper_reliday2 = mean(mean_reliday2) + 3*sd(mean_reliday2),
  )

# check how many there are
hedge_retest %>% 
  filter(mean_reliday1 >= mean(mean_reliday1) + 3*sd(mean_reliday1) | 
         mean_reliday1 <= mean(mean_reliday1) - 3*sd(mean_reliday1) |
         mean_reliday2 >= mean(mean_reliday2) + 3*sd(mean_reliday2) |
         mean_reliday2 <= mean(mean_reliday2) - 3*sd(mean_reliday2))

@@

```{r retest_hedge_kids}
hedge_retest_kids <- hedge_retest %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = ageInYears), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 4, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 4.1), breaks = seq(0, 4, 1)) +
  scale_y_continuous(limits = c(0, 4.1), breaks = seq(0, 4, 1)) +
  labs(x = "Testday 1", y = "Testday 2")

@@

# run model
mRetestHedge <- brm(clickDistInBalloons ~ age + (0 + reliday | subjID), 
                              data   = mDataRetestHedge, 
                              family = lognormal(), 
                              warmup = 1000, 
                              iter   = 3000, 
                              chains = 4, 
                              inits  = "random",
                              cores  = 4)

write.csv(mRetestHedge, "../saves/mRetestHedge.csv", quote = F, row.names = F)
saveRDS(mRetestHedge, "../saves/mRetestHedge.rds")
```

@@

@@

# run model
mRetestBox <- brm(correctBox ~ age + (0 + reliday | subjID), 
                              data   = mDataRetestBox, 
                              family = bernoulli(link = "logit"),
                              warmup = 1000, 
                              iter   = 3000, 
                              chains = 4, 
                              inits  = "random",
                              cores  = 4)

write.csv(mRetestBox, "../saves/mRetestBox.csv", quote = F, row.names = F)
saveRDS(mRetestBox, "../saves/mRetestBox.rds")
```

@@
